---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# EndoTools

<!-- badges: start -->
[![R-CMD-check](https://github.com/TalhoukLab/EndoTools/workflows/R-CMD-check/badge.svg)](https://github.com/TalhoukLab/EndoTools/actions)
[![Codecov test coverage](https://codecov.io/gh/TalhoukLab/EndoTools/branch/master/graph/badge.svg)](https://codecov.io/gh/TalhoukLab/EndoTools?branch=master)
<!-- badges: end -->

The goal of EndoTools is to provide helper tools for calculating commonly used variables in endometrial cancer projects such as:

- MMR
- ProMisE
- ESMO

There are different versions for each molecular variable.

## Installation

You can install EndoTools from GitHub with:

``` r
# install.packages("remotes")
remotes::install_github("TalhoukLab/EndoTools")
```

## Example

This is a basic example which shows you how to assign and compare different ESMO risk groups:

```{r example, message=FALSE}
library(EndoTools)
library(dplyr)

df <- emdb %>%
  mutate(
    eclass2 = assign_promise2019(mmr_ihc_2, pole_mut, p53),
    esmo2013 = assign_esmo2013(stage_full, grade_rev, hist_rev_gr),
    esmo2016 = assign_esmo2016(stage_full, grade_rev, hist_rev_gr, myo, lvi),
    esmo2020 = assign_esmo2020(stage_full, grade_rev, hist_rev_gr, myo, lvi, eclass2,
                               residual)
  )

df %>% 
  count(esmo2013)

df %>% 
  count(esmo2016)

df %>% 
  count(esmo2020)

df %>% 
  count(esmo2013, esmo2016, esmo2020)
```
